quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays

### 2025-01-10 man/manuscript/manuscript.qmd
Added a function for calculating thresholds.

>>>>

### Thresholds
Many publications have different methods of determining thresholds. By and large, the most popular method is to take the average background fluorescence of the entire plate and add some multiple of standard deviations. The quicR package provides the "calculate_threshold" function for this purpose. A value can be provided as the optional argument, "multiplier", which will be applied to the standard deviation.
```{r, eval=FALSE}
get_real(file)[[1]] %>% calculate_threshold(multiplier = 10)
```
```{r, echo=FALSE}
calculate_threshold(df_, multiplier = 10)
```
